The Units of Permissionless Consensus: \\ Towards Mobile and Edge Computing

### 2022-10-31 theoretical-consensus/article/article.tex
add presentation

\subsubsection{Proof-of-Location} may be an alternative for envisioning a future where the
consensus is achieved by taking advantage of the dynamism and easiness of movement, placement and 
tracking of smaller and more location-versatile devices, such as mobile phones, IoT devices, etc.
The idea behind this approach is to use the location and the movement of the devices 
as a proof for the consensus. It relies on the location validation by close proximity, 
for example, using low-range communication channels, either by proving the location
of the device at a certain point in time, or by proving their proximity to other devices.
Incentive mechanisms may play an important role to prevent location spoofing, collusion, etc. \cite{natoli2019deconstructing}.
This protocol is getting increased attention, especially in the context of IoT, 
with the provision of decentralized, permissionless and autonomous networks of 
low-powered devices that can be used for providing these location verification services \cite{9376868}.

@@

\subsubsection{The XRP Ledger Consensus Protocol} powers the XRP Ledger in a
low-latency, high throughput, and  BFT fashion. The network itself operates somewhat
differently from the other blockchain references, and treats transactions as atomic units of 
the ledger. These transactions are collected by the nodes and relayed to the
nodes' UNL (Unique Node List), which is a list of peers that are trusted by that current
entity. At every epoch, multiple rounds are needed to filter transactions and vote 
on the next state of the ledger. This voting happens at the 
UNLs' level, which are expected to be overlapped by a certain percentage,
in order to achieve the artificial vote threshold for globally accepting the transactions.
That threshold defines the fault tolerance of the protocol, and is set to 80\%, which 
bounds this protocol to a 1/5 BFT allowance \cite{schwartz2014ripple, chase2018analysis}. 
Despite that limitation, when compared to other BFT protocols, this protocol seeks to trade 
fault tolerance for performance, by having lower connectivity and less message exchanges. 
However, it is still expected high synchrony within the UNLs. Given these characteristics, the protocol
is expected to be more suitable for permissioned networks, and, in terms of network size,
is seen as not as scalable and decentralized as the permissionless ones \cite{survey-dist-consensus}.

>>>>

\subsubsection{Proof-of-Location} may be an alternative for envisioning a future where the
consensus is achieved by taking advantage of the dynamism and easiness of movement, placement and 
tracking of smaller and more location-versatile devices, such as mobile phones, IoT devices, etc.
The idea behind this approach is to use the location and movement of these devices 
as a proof for the consensus. It relies on the location validation by close proximity, 
for example, using low-range communication channels, either by proving the location
of the device at a certain point in time, or by proving their proximity to other devices.
Incentive mechanisms may play an important role to prevent location spoofing, collusion, etc. \cite{natoli2019deconstructing}.
These protocols are getting increased attention, especially in the context of IoT, 
with the provision of decentralized, permissionless and autonomous networks of 
low-powered devices that can be used for providing location verification services \cite{9376868}.

@@

\subsubsection{The XRP Ledger Consensus Protocol} powers the XRP Ledger in a
low-latency, high throughput, and  BFT fashion. The network itself operates somewhat
differently from the other blockchain references, and treats transactions as atomic units of 
the ledger. These transactions are collected by the nodes and relayed to the
nodes' UNL (Unique Node List), which is a list of peers that are trusted by that current
entity. At every epoch, multiple rounds are needed to filter transactions and vote 
on the next state of the ledger. This voting happens at the 
UNLs' level, which are expected to be overlapped by a certain percentage,
in order to achieve the artificial vote threshold for globally accepting the transactions.
That threshold defines the fault tolerance of the protocol, and is set to 80\%, which 
bounds this protocol to a 1/5 BFT allowance \cite{schwartz2014ripple, chase2018analysis}. 
Despite that limitation, when compared to other BFT protocols, this protocol seeks to trade 
fault tolerance for performance, by having lower connectivity and less message exchanges. 
However, it is still expected high synchrony within the UNLs. Given these characteristics, this protocol
may be more suitable for permissioned networks, and, in terms of network size,
is seen as not as scalable and decentralized as the permissionless ones \cite{survey-dist-consensus}.
